---
title: "Case_Study"
author: "Jana Lee"
date: "10/8/2019"
output: html_document
---
Load in packages:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)
library(leaflet)
```


```{r}
library(p8105.datasets)
data(nyc_airbnb)
view(nyc_airbnb)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

Brainstorming questions:
* how are airbnb prices related to rent in the neighborhood?
* which neighborhood is most expensive and which is cheapest?
* do hosts with multiple sites have higher prices or ratings?
* does price have any relation to ratings?
* average length of stay related to neighborhood? price? etc?

## Exploratory Question: Which neighborhood is most expensive and which is cheapest in Manhattan?
```{r}
airbnb_manhattan = 
  nyc_airbnb
```

Renaming some variables for ease
```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(
    stars = review_scores_location / 2,
    borough = neighbourhood_group
  )
```


Playing with Code from Class:
```{r}
nyc_airbnb %>%
 mutate(neighbourhood = as.factor(neighbourhood)) %>%
  filter(borough == "Manhattan") %>% 
 ggplot(aes(x=price, y=neighbourhood)) +
 geom_violin()
```

```{r}
price_neighborhood = select(nyc_airbnb,neighbourhood, price) %>%
 group_by(neighbourhood) %>%
 summarise(
   mean_price = mean(price)
 ) %>%
 arrange(
   -mean_price
 )
 price_neighborhood[1,1]
 price_neighborhood[217,1]
```

```{r}
nyc_airbnb %>% 
  group_by (borough, room_type) %>% 
  summarize (med_price = median(price, na.rm = TRUE)) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = med_price
  )
```

```{r}
nyc_airbnb %>% 
  filter(borough == "Staten Island", room_type == "Shared room")
```

If we're going to look at this, we should know the sample size.
```{r}
nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

```{r}
nyc_airbnb %>% 
  group_by (borough, neighbourhood) %>% 
  summarize(
    mean_price = mean(price, na.rm=TRUE),
    mean_review = mean(review_scores_location, na.rm = TRUE)
  ) %>% 
  ggplot(aes(x = mean_review, y = mean_price)) + 
  geom_point() +
  facet_grid(~borough)
```


```{r}
nyc_airbnb %>% 
  count(neighbourhood)
```

Make similar plot! In Astoria, what is the stars and price relationship?
```{r}
nyc_airbnb %>% 
  filter(neighbourhood == "Astoria") %>% 
  ggplot(aes(x = stars, y = price)) + 
  geom_point()
```

## Spatial locations
```{r}
#rentals located
nyc_airbnb %>%
  filter(borough == "Manhattan",
         price < 1000) %>% 
 ggplot(aes(x = lat, y = long, color = price)) +
 geom_point(alpha = .3) +
  facet_grid(~room_type)
```

## Leaflet introduction
Leaflet = trying to create maps and instigating a blank map. Add in tiles and you will get a map.
```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$stars)

nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    price > 2000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1)

# sample_n() = given this dataset, find a sample of this size
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  mutate(
    label = str_c("<b>Stars:", stars, "<b><b>Price:", price, sep = "")
  ) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(
    ~lat, ~long,
    color = ~pal(stars),
    radius = 1,
    popup = ~label)
```

